---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# caret.ts: time series models for the "caret" package

[![Build Status](https://travis-ci.org/sfeuerriegel/caret.ts.svg?branch=master)](https://travis-ci.org/sfeuerriegel/caret.ts)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/caret.ts)](https://cran.r-project.org/package=caret.ts)
[![Coverage Status](https://img.shields.io/codecov/c/github/sfeuerriegel/caret.ts/master.svg)](https://codecov.io/github/sfeuerriegel/caret.ts?branch=master)

**caret.ts** provides various functions for machine learning with time series data. While the "caret" package is common in various tasks related to machine learning; its naive version does yet ship dedicated time series models. This implementation thus extends the "caret" package and offers additional models, including ARMA or ARIMA. Additionally, it customizes the "train" function to accept time series data. 

## Overview

The most important functions in **caret.ts** are:

* TODO. 

To see examples of these functions in use, check out the help pages, the demos and the vignette. 


## Installation

Using the **devtools** package, you can easily install the latest development version of **caret.ts** with

```{r,eval=FALSE}
install.packages("devtools")

# Option 1: download and install latest version from ‘GitHub’
devtools::install_github("sfeuerriegel/caret.ts")

# Option 2: install directly from bundled archive
# devtoos::install_local("caret.ts_0.1.0.tar.gz")
```

Notes: 

* In the case of option 2, you have to specify the path either to the directory of **caret.ts** or to the bundled archive **caret.ts_0.1.0.tar.gz**

* A CRAN version has not yet been released.

## Usage

This section shows the basic functionality of how to perform machine learning with time seris models inside **caret**. First, load the corresponding package **caret.ts**. 

```{r, message=FALSE}
library(caret.ts)
```

The examples below how to insert the models inside the `train()` function from **caret**. Additionally, this package also implements an additional variant of the `train()` function that accepts time series objects.

### ARMA model

Auto-regressive moving-average (ARMA) models can be faciliated both with and without exogeneous variables. By using `arma_model(p, q)`, one can construct an ARMA model of a fixed, pre-defined order. Alternatively, one can let the `train()` function pick the order that fits the training data best. For the latter purpose, use `auto_arma_model()` (with optional arguments for the maximum order).

**Example without exogenous variables:**

```{r}

```

**Example with exogenous variables:**

```{r}

```

Predictions and testing:

### ARIMA model

Auto-regressive moving-average models with differneces (ARIMA) also support exogeneous variables if desired. By using `arima_model(p, d, q)`, one can construct an ARIMA model of a fixed, pre-defined order:

* `p`: Order of auto-regressive (AR) terms

* `d`: Degree of differencing

* `q`: Order of moving-average (MA) terms

Alternatively, one can let the `train()` function pick the order that fits the training data best. For the latter purpose, use `auto_arima_model()` (with optional arguments for the maximum order).

**Example without exogenous variables:**

```{r, warning=FALSE, message=FALSE}
library(forecast)

data(WWWusage) # from package "forecast"
df <- data.frame(y = as.numeric(WWWusage))

library(caret)

# ARIMA model of order (1, 1, 1)

arima1 <- train(y ~ 1, data = df, method = arima_model(1, 1, 1), trControl = trainDirectFit())

summary(arima1)

predict(arima1, df) # in-sample predictions
RMSE(predict(arima1, df), df) # in-sample RMSE

# ARIMA model of order (1, 2, 1)

arima2 <- train(y ~ 1, data = df, method = arima_model(1, 2, 1), trControl = trainDirectFit())

summary(arima2)

predict(arima2, df) # in-sample predictions
RMSE(predict(arima2, df), df) # in-sample RMSE

# Auto-tuned ARIMA model

auto_arima <- train(y ~ 1, data = df, method = auto_arima_model(), trControl = trainDirectFit())

summary(auto_arima)
arimaorder(auto_arima$finalModel) # order of best model

predict(auto_arima, df) # in-sample predictions
RMSE(predict(auto_arima, df), df) # in-sample RMSE
```

**Example with exogenous variables:**

```{r warning=FALSE, message=FALSE}
library(vars)
data(Canada)

arima <- train(x = Canada[, -2], y = Canada[, 2], 
               method = auto_arima_model(), trControl = trainDirectFit())

summary(arima)
arimaorder(arima$finalModel) # order of best model

predict(arima, Canada[, -2]) # in-sample predictions
RMSE(predict(arima, Canada[, -2]), Canada[, 2]) # in-sample RMSE
```

Predictions and testing:

### Variable importance

Variable importance metrics as provided by **caret** are supported accordingly. 

**Example:**

```{r varimp}
absCoef <- varImp(arima, scale = FALSE) # variable importance (= absolute value of coefficient)
absCoef

plot(absCoef)
```


### Alternative interface for training with time series objects

`trainDirectFit()`

This package automatically extends the `train()` function to successfully work with time series objects of class `ts`.

**Example with uni-variate time series:**

```{r}
class(WWWusage)
str(WWWusage)

# Example with uni-variate time series and no predictors

arima <- train(WWWusage, method = auto_arima_model(), trControl = trainDirectFit())

summary(arima)
arimaorder(arima$finalModel) # order of best model

predict(arima, WWWusage) # in-sample RMSE
RMSE(predict(arima, WWWusage), WWWusage) # in-sample RMSE
```

**Example for time series with exogenous predictors:**

```{r}
class(Canada)
str(Canada)

# Variant with explicit x and y

arima <- train(x = Canada[, -2], y = Canada[, 2], 
               method = auto_arima_model(), trControl = trainDirectFit())

summary(arima)
arimaorder(arima$finalModel) # order of best model

predict(arima, Canada[, -2]) # in-sample predictions
RMSE(predict(arima, Canada[, -2]), Canada[, 2]) # in-sample RMSE

# Variant with formula

arima <- train(form = prod ~ ., data = Canada, 
               method = auto_arima_model(), trControl = trainDirectFit())

summary(arima)
arimaorder(arima$finalModel) # order of best model

predict(arima, Canada) # in-sample predictions
RMSE(predict(arima, Canada), Canada[, "prod"]) # in-sample RMSE
```


## License

**caret.ts** is released under the [MIT License](https://opensource.org/licenses/MIT)

Copyright (c) 2016 Stefan Feuerriegel